### 2019-11-20 Manuscript/Manuscript.tex
Updates from Overleaf

>>>>

It is sometimes argued that hypotheses that invoke enhanced weathering in regions of active uplift predict an increase in global alkalinity fluxes. However, global alkalinity delivery from silicate weathering needs to be nearly constant to keep the long-term carbon cycle in steady-state. Enhanced weathering in a region such as the SEAI is compensated by a decrease in weathering in other regions where there has not been tectonically-forced change. Global alkalinity delivery from silicate weathering does not change, but occurs more efficiently and thereby at lower \pCOtwo. However, given that carbonate weathering is disconnected from long-term carbon-cycle mass balance, alkalinity delivery from carbonate weathering could change in an evolving climate and be observable in proxy records \cite{Si2019a}.
